---
title: "Título"
author: "Autor"
date: "7 de agosto de 2019"
output: pdf_document
mainfont: Times New Roman      # fonte Times New Roman
fontfamily: mathpazo                 # letra serifada
fontsize: 12 pt                           # tamanho da fonte
spacing: double                         # espaçamento entre linhas; double ou single
indent: true                               # indentação nos parágrafos
---

########################## UFPE - MESTRADO - PPGCP #####################################
##################### TRABALHO FINAL - ANLISE DE DADOS #################################
####################### PROFESSOR: DAVI MOREIRA ########################################
#################### ALUNA: NATHALIA VIVIANI BITTENCOURT ###############################
########################### TRATAMENTO DOS DADOS #######################################

# carregar pacotes

```{r}
if(require(stargazer) == F) install.packages('stargazer'); require(stargazer) 
library(stringi); library(stringr); 
library(dplyr); library(readxl)
```

# carregar dados

```{r}
face <- read_excel("dados/facebook_2019.xlsx")
face2 <- read_excel("dados/world_leaders_followers_atualizado.xlsx")
pop_speech <- read.csv("dados/pop_speech_clean.csv")
```

#===================================#
# tratamento de dados
#==================================#

#### facebook 2019

# filtrar selecionar na base do facebook
```{r}
face = face[face$`Personal Profile` == 1,]
```


# tirar nomes 'president' e 'prime minister'
```{r}
face$leader = str_replace(face$`Page Section`, 'President ', '')
face$leader = str_replace(face$leader, 'Prime Minister ', '')
```


# remover caracteres para padronizacao e combinacao
```{r}
face$leader = stri_trans_general(face$leader, "latin-ascii")
face$leader = tolower(face$leader)
face$leader = str_replace(face$leader, '-', ' ')
```

#### world leaders followers atualizado

# renomear colunas a partir da linha 2 e remover linha 1
```{r}
colnames(face2) = face2[2,]
face2 = face2[-c(1:2),]
```

# transformar likes em numerico

```{r}
face2$Likes = as.numeric(face2$Likes)
```

# remover caracteres para padronizacao e combinacao
```{r}
face2$leader = stri_trans_general(face2$`World Leader`, "latin-ascii")
face2$leader = tolower(face2$leader)
face2$leader = str_replace(face2$leader, '-', ' ')
```

#=====================#
# combinar dados
#====================#

# selecionar variaveis de interesse
```{r}
face = face[,c('leader','Likes')]
face2 = face2[,c('leader','Likes')]
```

# concatenar com a base facebook19
```{r}
dataface = rbind(face, face2)
```

# remover casos dusplicados e casos faltantes 
```{r}
dataface = dataface[!duplicated(dataface$leader),]
dataface = dataface[complete.cases(dataface$Likes),]
```

# combinar dados
```{r}
dataset = merge(pop_speech, dataface, by='leader')
```

# selecionar variaveis e renomear
```{r}
dataset = dataset[,c('leader', 'Likes','average.score', 'speech.category', 'region')]
colnames(dataset) = c('leader', 'face_likes','average_score' ,'speech', 'region')
```

#Salvando a nova base em formato csv e xlsx
```{r}
write.csv(dataset, 'dataset_cru.csv', row.names = F)
```


########################## UFPE - MESTRADO - PPGCP #####################################
##################### TRABALHO FINAL - ANLISE DE DADOS #################################
####################### PROFESSOR: DAVI MOREIRA ########################################
#################### ALUNA: NATHALIA VIVIANI BITTENCOURT ###############################
#################################### MODELS ############################################

#Downloading Packages
```{r}
getwd()
library(readxl); library(stringi); library(stringr); 
library(tidyverse); library(stargazer)
library(readxl)
```



# Downloading final treated data - check tratamento.R  
```{r}
data <- read_excel("dataset.xlsx")
```

# Two Plots to understand the data:
```{r}
library(ggplot2)
ggplot(data = data, aes(x=leader, y=average_score)) +
  geom_col(fill = "#329999") +
  labs(title = "Pop_Speech_Dataset", x='leader', y= 'populism score') +
  theme_minimal() +
  coord_flip()

ggplot(data = data, aes(x=leader, y=face_likes)) +
  geom_col(fill = "#68132e") +
  geom_label(aes(label=face_likesc)) +
  labs(title = "Dataset_Face_Likes", x='leader', y= 'Likes') +
  theme_minimal() +
  coord_flip()
```

#Now, we execute the function mutate in order to creat the variables to our models:

# Variable Pop_VeryPop that creates a new column to separate populists and very populists from the other leaders
```{r}
data <- mutate(data, Pop_VeryPop = ifelse(speech == "Populist" | speech == "Very Populist", 1, 0))
```

#Variable Pop_VeryPop_SomewPop that creates a new column to separate all kinds of populists from no populists at all
```{r}
data <- mutate(data, Pop_VeryPop_SomewPop = ifelse(speech == "Populist" | 
                                            speech == "Very Populist" |
                                            speech == "Somewhat populist", 1, 0))
```


#Variable Not_populist that creates a new column to separate not populist leaders
```{r}
data <- mutate(data, Not_populist = ifelse(speech == 'Not populist', 1, 0)) 
```

#Variable America that creates a new column to separate the two regions in analysis
```{r}
data <- mutate(data, America = ifelse(region == "Latin America & Caribbean" |
                                        region == "North America", 1, 0))
```

#Variable Europe_CentralAsia that creates a new column to separate the two regions in analysis
```{r}
data <- mutate(data, Europe_CentralAsia = ifelse(region == "Europe & Central Asia", 1, 0))
```


###### At last, the Models ########

# First Linear model: vd: face_likes; vi: Pop_VeryPop

```{r}
Reg1_Pop_VeryPop = glm(face_likes ~ Pop_VeryPop, data = data)
summary(Reg1_Pop_VeryPop)
layout(matrix(c(1,2,3,4),2,2))
plot(Reg1_Pop_VeryPop)

#Interactive Regression plot:
install.packages('ggiraphExtra') 
require(ggiraph)
require(ggiraphExtra)
require(plyr)
ggPredict(Reg1_Pop_VeryPop,se=TRUE,interactive=TRUE)
```



# Second Linear model: vd: face_likes; vi: Pop_VeryPop_SomewPop
```{r}
Reg2_Pop_VeryPop_SomewPop = glm(face_likes ~ Pop_VeryPop_SomewPop, data = data)
summary(Reg2_Pop_VeryPop_SomewPop)
layout(matrix(c(1,2,3,4),2,2))
plot(Reg2_Pop_VeryPop_SomewPop)

#Interactive Regression plot:
require(ggiraph)
require(ggiraphExtra)
require(plyr)
ggPredict(Reg2_Pop_VeryPop_SomewPop,se=TRUE,interactive=TRUE)
```



# Third Linear model: vd: face_likes; vi: Not_populist
```{r}
Reg3_Not_populist = glm(face_likes ~ Not_populist, data = data)
summary(Reg3_Not_populist)
layout(matrix(c(1,2,3,4),2,2))
plot(Reg3_Not_populist)

#Interactive Regression plot:
require(ggiraph)
require(ggiraphExtra)
require(plyr)
ggPredict(Reg3_Not_populist,se=TRUE,interactive=TRUE)
```


# Multiple Linear Regression

## First Model: vd: face_likes; vi: Pop_VeryPop_SomewPop, vii: America
```{r}
RegM1_America <- lm(face_likes ~ America + Pop_VeryPop_SomewPop, data = data)
summary(RegM1_America)
layout(matrix(c(1,2,3,4),2,2))
plot(RegM1_America)

#Interactive plot 1:
ggPredict(RegM1_America,colorAsFactor = TRUE,interactive=TRUE)
```



##Second Model: vd: face_likes; vi: Pop_VeryPop_SomewPop, vii: Europe_CentralAsia

```{r}
RegM2_Europe_CentralAsia <- lm(face_likes ~ Europe_CentralAsia + Pop_VeryPop_SomewPop, data = data)
summary(RegM2_Europe_CentralAsia)
layout(matrix(c(1,2,3,4),2,2))
plot(RegM2_Europe_CentralAsia)

#Interactive plot 2:
ggPredict(RegM2_Europe_CentralAsia,colorAsFactor = TRUE,interactive=TRUE)
```


# Comparative analysis between the two models:
```{r}
anova(RegM1_America, RegM2_Europe_CentralAsia)
```

# Stargazer tables in order to best interpret the results:

#Linear Regression - comparative summary

```{r}
library(stargazer)
stargazer(Reg1_Pop_VeryPop, Reg2_Pop_VeryPop_SomewPop, Reg3_Not_populist,
          type = "html", title = "Results", style = "ajps", p.auto=FALSE,  out="linearmodels.htm",
          covariate.labels = c("|Populist + Very Pop.|", "|Populist + Very Pop. + Somew. Pop.|", "|Not Populist"))
```


#Multiple Linear Regressions - comparative summary and graphs

```{r}
stargazer(RegM1_America, RegM2_Europe_CentralAsia,
          type = "html", title = "Results 2", style = "ajps", p.auto=FALSE, out="multiplemodels.htm",
          covariate.labels = c("|America|", "|Europe and Central Asia|")) 
```

```{r}
install.packages('ggiraphExtra') 
require(ggiraph)
require(ggiraphExtra)
require(plyr)
ggPredict(Reg1_Pop_VeryPop,se=TRUE,interactive=TRUE)
```






